---
title: "Facebook Social Network Analysis"
output: 
    html_notebook:
        theme: flatly
---

### Load Packages

```{r, warning=FALSE, message=FALSE}
require(igraph)
require(dplyr)
require(RColorBrewer)
```

### Read Data

```{r}
nodes <- read.table("nodes.txt", sep="\t", header = TRUE, stringsAsFactors = FALSE)
edges <- read.table("edges.txt", sep="\t", header = TRUE)

head(nodes)
```


```{r}
head(edges)
```

```{r}
nrow(edges)
```

### Create Graph

```{r}
fb <- graph_from_data_frame(edges,directed=FALSE)
plot(fb)
```

```{r, fig.width = 20}
plot(fb, vertex.label = NA, vertex.size = 3)
```

### Remove my Node

```{r}
nodes <- filter(nodes, Node != 'n0')
edges <- edges %>% filter(Source != 'n0' & Target != 'n0')

nrow(edges)
```


```{r, fig.width = 20}
set.seed(1)
fb <- graph_from_data_frame(edges,directed=FALSE)
plot(fb, vertex.label = NA, vertex.size = 3)
```

### Calculate Centrality Measures

```{r}
dC <- degree(fb)
bC <- betweenness(fb)
cC <- closeness(fb)

centDF <- data.frame(Node = names(dC), dCent = unname(dC), bCent = unname(bC), cCent = unname(cC), 
                     stringsAsFactors = FALSE)

nodes <- left_join(nodes, centDF, by='Node')
nodes
```


```{r}
summary(nodes)
```

Visualize centrality measures. 

```{r, fig.width = 20}
ct <- cut(bC, c(-1,5,67,330,1000,50000), labels=FALSE)
myPal <- brewer.pal(5, "RdPu")

set.seed(1)
plot(fb, vertex.label = NA, vertex.size = ct, vertex.color = myPal[ct])
```

```{r, fig.width = 20}
ct <- cut(bC, c(-1,1000,20000, 50000), labels=FALSE)
myPal <- brewer.pal(3, "RdPu")

set.seed(1)
plot(fb, vertex.label = NA, vertex.size = 2+ct, vertex.color = myPal[ct])
```

Find the nodes with the highest betweeness centrality.

```{r}
arrange(nodes, desc(bCent))
```

Find the nodes with the highest degree centrality.

```{r}
arrange(nodes, desc(dCent))
```

Find the nodes with the highest closeness centrality.

```{r}
arrange(nodes, desc(cCent))
```

### Community Detection

```{r, fig.width = 20}
ceb <- cluster_edge_betweenness(fb)

set.seed(1)
plot(ceb, fb, vertex.label = NA, vertex.size = 3)
```


```{r}
length(ceb)
```

```{r}
mem <- membership(ceb)
commDF <- data.frame(Node = names(mem), Comm = as.vector(unname(mem)), stringsAsFactors = FALSE)

nodes <- left_join(nodes, commDF, by='Node')
nodes

```


```{r}
nodes %>%
  group_by(Comm) %>%
  count() %>%
  arrange(desc(n))
```

```{r}
nodes %>% filter(Comm == 1) %>% arrange(desc(bCent))
```



<center>
Community | Size | Description
-----|-----|----------------------------------------------
1 | 184 | People from MST.
6 | 48 | Close friends from MST.
5 | 47 | My family.
8 | 45 | My wife's family and friends. 
2 | 43 | People from HS.
4 | 13 | PSU students. 
16 | 11 | LU students.
9 | 6 | Rock climbers.
11 | 6 | People from 6 South. 
15 | 6 | PSU students.
7 | 5 | Rolla townies. 
13 | 4 | PSU students.
18 | 4 | PSU faculty. 
10 | 3 | Advisor and his family. 
3 | 2 | PSU students. 
14 | 2 | Vegans. 
19 | 1 | MST student.
12 | 1 | MST student. 
17 | 1 | Friend of my wife. 
20 | 1 | MST student. 
21 | 1 | MST student. 
22 | 1 | MST grad student. 
</center>

```{r, fig.width = 20}
set.seed(1)
plot(fb, vertex.label = mem, vertex.size = 5)
```


```{r, fig.width = 20}
comm8 <- filter(nodes, Comm == 8)
g8 <- induced.subgraph(fb, vids = comm8$Node) 
plot(g8)
```



```{r}
sel<- V(g8)$name

selDF <- data.frame(Node = sel, stringsAsFactors = FALSE)
selDF <- left_join(selDF, nodes, by='Node')

selDF
```


```{r, fig.width = 20}
plot(g8, vertex.label = selDF$Name, vertex.label.cex = 1.5)
```


### Find cliques


```{r}
lc <- largest_cliques(fb)
lc
```

```{r}
c1 <- lc[[1]]$name
filter(nodes, Node %in% c1)
```


```{r}
c2 <- lc[[2]]$name
filter(nodes, Node %in% c2)
```

```{r}
c3 <- lc[[3]]$name
filter(nodes, Node %in% c3)
```


```{r}
mc <- max_cliques(fb, min = 10)
sapply(mc, length)
```


```{r}
filter(nodes, Node %in% mc[[1]]$name)
```
































